Globally-centered autocovariances in MCMC

### 2020-08-31 Paper/main.tex
Final appendix edits

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(+ \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

@@

Consider pseudo autocovariance and spectral variance estimators for the $s$th chain, denoted by $\tilde{\Upsilon}_s(k)$ and $\tilde{\Sigma}_s$ that use data centered around the unobserved actual mean $\mu$:
\begin{align*}
    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t \in I_k}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
\end{align*}
%
The average pseudo spectral variance estimator is
\[
\tilde{\Sigma}_A = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
\]

@@

We first present a result which will be useful to use later. For any Markov chain $s$, 

@@

   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-k} \dfrac{1}{n}\left[ \left(X_{st} - \mu_g \right)_i  \left(\mu_g-\bar{\bar{X}} \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu_g \right)_j\right]\right\}\right| \\
   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-k} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-k} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\

@@

    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\

@@

% \begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
 Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
\begin{equation}
\label{eq:G-SVE_asv_consis}
 \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
\end{equation}
We have shown from the proof of strong consistency that,
\begin{align*}
 &\left| \hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right|\\
 & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t \in I_k}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
& \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,,
\end{align*}
where $g_1(n), g_2(n), g_3(n)$ are defined such that as $n \to \infty$,  $g_1(n), g_2(n), g_3(n) \to 0$.
%\begin{align*}
%   g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
%    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
%    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
%\end{align*}
%

By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
\begin{align*}
\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
& \leq \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
& := g_n^*(Y_{11}, \dots, Y_{1n}, \dots, Y_{m1}, \dots, Y_{mn})\,.
\end{align*}
But since by assumption $\E D^4 <\infty$ and the fourth moment is finite,
\[
\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
\]
Thus, $\E \left| g_n^* \right| < \infty$ and further as $n \to \infty$, $g_n \to 0$ under the assumptions. Since $g_1, g_2, g_3 \to 0$, $\E g_n^* \to 0$. By the majorized convergence theorem \citep{zeid:2013}, as $n \to \infty$,
\begin{equation}
\label{eq:squared_mean_diff}
  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
\end{equation}
%
We will use \eqref{eq:squared_mean_diff} to show that the variances are equivalent. Define,
\[
\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
\]
We will show that the above is $o(1)$. Using Cauchy-Schwarz inequality followed by \eqref{eq:squared_mean_diff},
\begin{align*}
\left|  \xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\ 
& \leq \E\left[\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\ 
& = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) = o(1)\,.
\end{align*}
%
Finally,
\begin{align*}
 \Var\left(\hat{\Sigma}_{G}^{ij} \right)  & = \E \left[ \left(\hat{\Sigma}_{G}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
& = \E \left[ \left(\hat{\Sigma}_{G}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)^2 \right]\\
& = \E\left[ \left( \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)  \right)^2 \right] \\ 
& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right) \right)^2 \right] \\
& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)\right]\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)\,.
\end{align*}

@@

\section{Additional Examples}
We present two additional real-world examples to illustrate the advantage of global autocorrelation estimator using ACF plots. For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
% We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.  In this section we will use two real-life datsets to exemplify the better performance of our replicated autocovariance estimator for multiple Markov chains. R packages already exist to create Markov chains for these examples. However, when these chains are started from different points, we will observe that they do not represent the target distribution well for finite samples. The traditional empirical ACF estimator fails in these cases, whereas our estimator shows promising results. We will not engage into full error analysis for these examples due to computational restrictions posed by high dimensional sample space. 
\subsection{Bayesian Poisson Change Point Model}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
    \caption{Trace plot for second (left) and third (right) component of two chains started from random points. The two colors denote the two different chains.}
    \label{fig:poisson-trace}
\end{figure}
\begin{figure}[htbp]
    \centering
      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}  \\ \vspace{-.5cm}
      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
    \caption{Change point: ACF plots using local-centering (left) and global-centering (right) for $m=2$ parallel Markov chains. The individual chains are shown through dashed lines and average over $m$ chains is the solid line. The chain lengths are $n = 1000$ (top row) and $n = 10000$ (bottom row).}
    \label{fig:poisson-acf}
\end{figure}

Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF against locally-centered ACF in estimating the autocorrelations. For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highgly correlated. G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser samples per chain.

@@

We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking" which might cause formation of clusters in the social network. We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group, especially their grades. Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it. As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.

>>>>

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

@@

Consider pseudo autocovariance and spectral variance estimators for the $s$th chain, denoted by $\tilde{\Upsilon}_s(k)$ and $\tilde{\Sigma}_s$ that use data centered around the unobserved actual mean $\mu_g$:
\begin{align*}
    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t \in I_k}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
\end{align*}
%
The average pseudo spectral variance estimator is
\[
\tilde{\Sigma}_A = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
\]

@@

We first present a result which will be useful later. For any Markov chain $s$, 

@@

@@

    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\abs{\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)} < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\

@@

% \begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
 Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
\label{eq:G-SVE_asv_consis}
 \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
We have shown from the proof of strong consistency that,
 &\left| \hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right|\\
 & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t \in I_k}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
& \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,,
where it has been shown already that $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$. By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
& \leq \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
& := g_n^*(Y_{11}, \dots, Y_{1n}, \dots, Y_{m1}, \dots, Y_{mn})\,.
But since by assumption $\E D^4 <\infty$ and the fourth moment is finite,
\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
Thus, $\E \left| g_n^* \right| < \infty$ and further as $n \to \infty$, $g_n \to 0$ under the assumptions. Since $g_1, g_2, g_3 \to 0$, $\E g_n^* \to 0$. By the majorized convergence theorem \citep{zeid:2013}, as $n \to \infty$,
\label{eq:squared_mean_diff}
  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
We will use \eqref{eq:squared_mean_diff} to show that the variances are equivalent. Define,
\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
We will show that the above is $o(1)$. Using Cauchy-Schwarz inequality followed by \eqref{eq:squared_mean_diff},
\left|  \xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\ 
& \leq \E\left[\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\ 
& = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) = o(1)\,.
Finally,
 \Var\left(\hat{\Sigma}_{G}^{ij} \right)  & = \E \left[ \left(\hat{\Sigma}_{G}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
& = \E \left[ \left(\hat{\Sigma}_{G}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)^2 \right]\\
& = \E\left[ \left( \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)  \right)^2 \right] \\ 
& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right) \right)^2 \right] \\
& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)\right]\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)\,.

@@

\section{Additional Examples}
We present two additional real-world examples to illustrate the advantage of global autocovariance estimator using ACF plots. For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
% We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.  In this section we will use two real-life datsets to exemplify the better performance of our replicated autocovariance estimator for multiple Markov chains. R packages already exist to create Markov chains for these examples. However, when these chains are started from different points, we will observe that they do not represent the target distribution well for finite samples. The traditional empirical ACF estimator fails in these cases, whereas our estimator shows promising results. We will not engage into full error analysis for these examples due to computational restrictions posed by high dimensional sample space. 
\subsection{Bayesian Poisson Change Point Model}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
    \caption{Trace plot for second (left) and third (right) component of two chains started from random points. The two colors denote the two different chains.}
    \label{fig:poisson-trace}
\end{figure}
\begin{figure}[htbp]
    \centering
      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}  \\ \vspace{-.5cm}
      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
    \caption{Change point: ACF plots using local (left) and global (right) centering for $m=2$ parallel Markov chains. The individual chains are shown through dashed lines and average over $m$ chains is the solid line. The chain lengths are $n = 1000$ (top row) and $n = 10000$ (bottom row).}
    \label{fig:poisson-acf}
\end{figure}

Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF against locally-centered ACF in estimating the autocorrelations. For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highly correlated. G-ACF gives a more accurate estimation of autocorrelations in almost ten times lesser samples per chain.

@@

We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking". This might cause formation of clusters in the social network. We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group, especially their grades. Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it. As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.
